00-OD-preparation

### 2022-05-02 00-OD-preparation.Rmd
Completed impedance functions in 'draft-manuscript'. This .Rmd will eventually be moved to a new repository dedicated to manuscript writing when this MADRID-LEZ data package is complete.

zn <- st_read("data-raw/zn.shp")
```

@@

@@

```{r}
ggplot() +
  geom_sf(data = zn %>% filter(CC == 1), aes(fill = "City centre"), col = "green3") + # madrid city centre
  geom_sf(data = zn %>%  filter(LEZ == 1), aes(fill = "Low emission zone"), col = "red4") + #madrid low emission zone
  geom_sf(data = bbox_CityCentre, fill = NA, col = "black", size = 0.5)+
  scale_fill_manual(labels = c("City centre", "Low emission zone"),
                    values = c("green", "red")) + 
  annotation_scale(bar_cols = c("dimgrey", "white"), # scale bar for both the main plot and inset
                   height = unit(0.15, "cm"),
                   pad_y = unit(0.05, "cm")) +
  guides(fill=guide_legend(title=NULL)) +
  theme_void() + theme(legend.position = "none"
```

>>>>

zn <- st_read("data-raw/zn.shp")
ALLLEZ <- st_read("data-raw/Zona_Bajas_Emisiones_MADRID.shp")
```

@@

```{r}

ggplot() +
  geom_sf(data = zn) +
  geom_sf(data = ALLLEZ, fill="red") 
```

@@
